### 2016-05-19 plosOneJordanousKeller/rebuttal.txt

When submitting your revision, we need you to address these additional requirements.

Please ensure that your manuscript meets PLOS ONE's style requirements, including those for file naming. The PLOS ONE style templates can be found at

http://www.journals.plos.org/plosone/s/file?id=wjVg/PLOSOne_formatting_sample_main_body.pdf and http://www.journals.plos.org/plosone/s/file?id=ba62/PLOSOne_formatting_sample_title_authors_affiliations.pdf

***** ANNA TO DO For some reason, we've fallen foul of some of these, so I'll check that *****

@@

1.  We request that you please report additional details in your Methods:
i) A detailed overview of the search strategy used to identify papers for the creativity corpus and non-creativity corpus
ii) The specific methods for selecting papers, including inclusion and exclusion criteria
In addition, please include a figure of a flow diagram describing your search strategy (see http://prisma-statement.org/PRISMAStatement/FlowDiagram.aspx for examples)
We appreciate your attention to these requests."

*****
* We have added, as requested, the detailed overview of our search strategy and the methods/criteria for selecting papers. In particular we found that it was particularly helpful, for clarity, to frame our paper selection strategy in terms of inclusion/exclusion criteria. This is reported in text added in the Methods section. 
* Thank you for the link to the flow diagram examples.
***** PRISMA - ANNA TO DO THIS *****

### 2016-05-19 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
edit to methods section on search for papers

\textbf{The search strategy for identifying papers for the corpus was based around a literature search for the term `creativity' on the academic database {\em Scopus}. Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines. The inclusion criteria are as follows, listed in descending order of precedence: }
\begin{itemize}
\item \textbf{Papers must have, as their primary focus, discussion of the nature of creativity.}
\item \textbf{Papers should be considered particularly influential, as measured by the number of times it had been cited by other academic authors. For papers published in recent years and which have consequently not yet accrued many citations, selection was based on our subjective judgement of influence.}
\item \textbf{Papers selected should, as far as reasonable, represent a cross-section of years over the range 1950-2009. [The corpus was compiled in 2010.] 1950 was chosen as a starting point in recognition of the effect of J. P. Guilford's presidential address to the American Psychological Association \cite{guilford50}, which examined contemporary creativity research (or more specifically, the lack of thereof). His talk was highly influential in encouraging more creativity research activity \cite{kaufman09}. }
\item \textbf{Papers selected should, as far as reasonable, represent a cross-section of disciplines relevant to discussions of what creativity is. Fig. 1b. illustrates the disciplinary distribution of the corpus as it changes over the time period included in the corpus, according to journal disciplinary classification in the academic database {\em Scopus}, which classifies journals under their main subject area(s) covered. We should acknowledge here though that while many disciplines include work that applies information about creativity, often the focus is on application rather than in depth discussion of what creativity entails. Hence, while we sought to cover creativity from a broad range of perspectives, we also felt it was important not to compromise the key focus of our corpus as a representation of key discussions about the nature of creativity.}
\end{itemize}
\sout{The papers were carefully chosen so as to cover a wide range of years (1950-2009) and academic disciplines. A paper was included if it was considered particularly influential, as measured by the number of times it had been cited by other academic authors. For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.}

@@

@@

\subsection*{S2 Fig}
\label{S2_Fig}
{\bf Graph representation of the similarity of the nouns {\em concept} and {\em idea} and closely semantically related words. Each word is drawn as a node in the graph, linked together by a weighted edge representing the similarity of the two words (maximum similarity strength is 1.0).} 
%\begin{figure}[!ht]
% \begin{center}
%\includegraphics[scale=0.5]{images/conceptIdea}
% \end{center}
% \caption{Graph representation of the similarity of the nouns {\em concept} and {\em idea} and closely semantically related words. Each word is drawn as a node in the graph, linked together by a weighted edge representing the similarity of the two words (maximum similarity strength is 1.0).}
% \label{S2_Fig}
%\end{figure}

>>>>

\textbf{The search strategy for identifying papers for the corpus was based around a literature search for the term `creativity' on the academic database {\em Scopus}. This literature search was supplemented with other influential papers which may have not appeared in a Scopus search, such as a computational conference paper on cognitive models of creativity. (N.B. In Computer Science, a number of conferences carry as much or more publication weight as some journals). Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines. The inclusion criteria are as follows, listed in descending order of precedence: }
\begin{itemize}
\item \textbf{Papers must have, as their primary focus, discussion of the nature of creativity.}
\item \textbf{Papers should be considered particularly influential, as measured by the number of times it had been cited by other academic authors. For papers published in recent years and which have consequently not yet accrued many citations, selection was based on our subjective judgement of influence.}
\item \textbf{Papers selected should, as far as reasonable, represent a cross-section of years over the range 1950-2009. [The corpus was compiled in 2010.] 1950 was chosen as a starting point in recognition of the effect of J. P. Guilford's presidential address to the American Psychological Association \cite{guilford50}, which examined contemporary creativity research (or more specifically, the lack of thereof). His talk was highly influential in encouraging more creativity research activity \cite{kaufman09}. }
\item \textbf{Papers selected should, as far as reasonable, represent a cross-section of disciplines relevant to discussions of what creativity is. Fig. 1b. illustrates the disciplinary distribution of the corpus as it changes over the time period included in the corpus, according to journal disciplinary classification in the academic database {\em Scopus}, which classifies journals under their main subject area(s) covered. We should acknowledge here though that while many disciplines include work that applies information about creativity, often the focus is on application rather than in depth discussion of what creativity entails. Hence, while we sought to cover creativity from a broad range of perspectives, we also felt it was important not to compromise the key focus of our corpus as a representation of key discussions about the nature of creativity.}
\end{itemize}
\sout{The papers were carefully chosen so as to cover a wide range of years (1950-2009) and academic disciplines. A paper was included if it was considered particularly influential, as measured by the number of times it had been cited by other academic authors. For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.}

@@

\subsection*{S1a Fig}\label{S1a_Fig}
{\bf The 30 papers that make up the Creativity Corpus} 
%\begin{figure}
%\caption{The 30 papers that make up the Creativity Corpus}
% REMOVE IMAGES FROM SUBMITTED VERSION
%\includegraphics[width=\textwidth]{images/papersImage}
%\label{S1_Fig}
%\end{figure}

@@

\subsection*{S1b Fig}
\label{S1b_Fig}
{\bf Representation of the disciplinary breakdown of the Creativity Corpus by time period. Disciplines are as specified for the paper's journal, by the academic database {\em Scopus}. Note that Scopus may classify a journal under more than one discipline.} 
%\begin{figure}[!ht]
% \begin{center}
%\includegraphics[scale=0.5]{images/disciplines}
% \end{center}
% \caption{Representation of the disciplinary breakdown of the Creativity Corpus by time period. Disciplines are as specified for the paper's journal, by the academic database {\em Scopus}. Note that Scopus may classify a journal under more than one discipline.}
% \label{S1b_Fig}
%\end{figure}
